\documentclass{article}
% Packages
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}

% Format Sections
\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{\filcenter} [\titlerule]
	\titlespacing{\supsection}
	{0.2em} {0.2em} {0.2em}

\titleformat{\subsection}
{\bfseries}
{}
{1em}
{}
	\titlespacing{\subsection}
	{0.25em} {0.25em} {0.5em}

% Format Title
\renewcommand{\maketitle} {
	\begin{center}
	{\huge\bfseries
	\theauthor}

	Washington DC
	\end{center}


	Email: Jconroy12@gmail.com
	\hfill Phone: (202) 255 2703

	Github: github.com/Hannibal-ad-Portas
	\hfill Linkedin: linkedin.com/in/james-conroy-423288173
}

\author{James M. Conroy}
\title{R\'esum\'e}

\begin{document}
\maketitle
\section{Education}
\subsection{B.A. Computer Science \hfill  May 2019}
The Catholic University of America, Washington DC

\textbf {Relevant Coursework:}
Artificial Intelligence,
Unix Programming,
Computer Graphics,
Operating Systems,
Analysis of Algorithms,
Data Structures,
Software Engineering
\section{Senior Design Project}
My team created a system to find efficient pathways for autonomous ground vehicles, using an aerial drone.
The project involves Raspberry Pi's, Arduinos, and computer vision.
\section{Technical Skills}

\textbf{Languages}
c,
c++,
c\#,
Java,
Processing,
MATLAB,
SQL,
Python \\
\textbf{Tools}
Vim,
Git,
Windows,
Linux

\section{Projects}

\subsection{Grid Search on a Cost Map \hfill March 2019}
This project uses a variety of search algorithms to find a path from the start to the goal.
The algorithms used are:
Breath First Search,
Depth First Search,
and
A*.
\subsection{Queen Teams Problem \hfill February 2019}
This project finds a configuration where no queen threatens an enemy queen.
The project uses a hill climbing algorithm to find the solution.
Made using c++.

\subsection{K-Distance Domination \hfill April 2018}
This project generates a random vertex edge graph and then finds the set of nodes within k steps from any node.
Made using Processing.

\subsection{Cube Quest \hfill November 2016}
I contributed the environment for this student made computer game.
The project was made using the OpenGL library for Java.


\section{Work Experience}
\subsection{Technology Services \hfill Fall 2015 to Present}
Employed by The Catholic University of America,
I provided technical support for users over the phone, via email, and in person.
The support includes but is not limited to:
resetting passwords,
installing software,
installing computers,
installing new hardware in computers,
and
connecting computers to the campuses Active Directory.

\subsection{Technology Center Instructor \hfill Summer 2016}
Employed by the Boy Scouts of America, Mason Dixon Council Hagerstown, PA Sinoquipe Scout Reservation,
I instructed 4 merit badge session, leading hundreds of scouts to earn the
Personal Management,
Space Exploration,
and
Electronics
merit badges.
\subsection{Technology Center Director \hfill Summer 2015}
Employed by the Boy Scouts of America, Mason Dixon Council Hagerstown, PA Sinoquipe Scout Reservation,
I set up and ran the technology program for the camp season,
lead three merit badge sessions,
and managed two staff members.
\section{Awards and Honors}
\subsection{Eagle Scout \hfill 2012}
\subsection{Nominated for CUA Student Worker of the Year \hfill 2018}
\subsection{Nominated for best Undergraduate Project at CUA Research Day \hfill April 2018}
\subsection{Cash award winning AARP's Fraud Watch Network's Hackathon\hfill February 2017}
\subsection{Sinoquipe Scout Reservation -- Honor Staff Award \hfill August 2016}
\subsection{Sinoquipe Scout Reservation -- Program Director Award of Recognition \hfill August 2016}
\subsection{Sinoquipe Scout Reservation -- Camp Director Award of Recognition \hfill August 2016}
\subsection{CUA Scholarship }
\end{document}
